### 2025-04-08 Paper.tex
changes

@@

%==============================================
%================ Evaluation ===================
%==============================================
\section*{Evaluation}

\subsection*{DiffSinger}
The base model we used for our training and synthesizing is DiffSinger. It is an
acoustic model, meaning it can map linguistik and symbolic input (like text or
notes) into acoustic features, used to generate actual audio. Acoustic features
include the most common feature mel-spectograms, but can also include linear
spectograms, F0 and pitch contour, and energy. It is also a variance model,
which is needed when trying to synthesize actual singing. A variance model
models the acoustic variations, for example pitch, energy and duration of sound.
The variance model predicts, based on the training data, how the voice features
should vary over time, based on the input. To avoid long computation time and
large resource needs, DiffSinger uses a shallow diffusion model. Traditional
diffusion models generate data, by starting with pure, random noise, and step by
step denoising it. This inference process is slow and takes many steps for just
a single generated sample. The shallow diffusion model used by DiffSinger is a
simpler and faster version of a full diffusion model. It uses fewer steps, but
often starts with a better starting point (for example a prediction from another
model). DiffSinger uses a non-diffusion model to predict a rough mel-spectogram
for the synthesized data, and refines it using the shallow diffusion model. By
using this technique, a lot of unnecessary steps, resources and computation time
are saved. Not using another model to make a first prediction would cause the
generated data to be a lot worse, since less steps are used and therefore less
noise is removed.

\subsection*{Choosing a model}

@@

\subsection*{Used files}
The following 14 segments were used in the evaluation:
\begin{itemize}
    \item Segment 22 from album 1, song 4
    \item Segment 3 from album 1, song 5
    \item Segment 1 from album 1, song 8
    \item Segment 22 from album 1, song 8
    \item Segment 5 from album 2, song 4
    \item Segment 7 from album 2, song 6
    \item Segment 17 from album 2, song 6
    \item Segment 1 from album 2, song 9
    \item Segment 7 from album 2, song 9
    \item Segment 3 from album 3, song 5
    \item Segment 13 from album 3, song 5
    \item Segment 1 from album 3, song 6
    \item Segment 10 from album 3. song 6
    \item Segment 8 from album 5, song 3
\end{itemize}

\subsection*{Criteria}

@@

\subsubsection*{Perceptual Evaluation of Speed Quality (PESQ)}
While the evaluation using SingMOS is considered a subjective evaluation, PESQ
is an objective Mean Opinion Score evaluation. The result of PESQ is usually a
score of the perceived speech quality on a scale of 1.0 to 4.5 (with narrowband,
4.64 with wideband), with a value of <2.0 representing a poor perceived speech
quality, which may be hard to understand. A value of about 3.0 is considered a
fair quality with some degradation, but generally understandable, and a value of
4.0 or more is considered excellent quality, with (almost) no degradation.
Although PESQ itself aligns both input files to account for timing mismatches,
it should be irrelevant in our case, as both input files are supposed to have
the same text, and everything was already aligned previously. The perceptual
part in PESQ refers to the way the sound files are analyzed. Instead of treating
every frequency and loudness the same, PESQ mimics the human ear and how an ear
is more sensitive to certain frequencies. The reference value for identical
files (comparing the original sound files with themselves), is approximately 4.64, as
expected.

\subsubsection*{PESQ results}
\begin{figure}[hbtp]
    \includegraphics[width=\textwidth]{evaluation/graphs/PESQ.png}
    \caption{Perceptual Evaluation of Speech Quality results per model}
    \label{fig:pesq_results}
\end{figure}

@@

\subsubsection*{F0 Root mean square error (F0 RMSE)}
The F0 value of speech, often also referred to as pitch or fundamental
frequency, is measured in Hertz, and describes the rate of vibration of the
vocal folds. The range of F0 is usually between 50 Hz to 450 Hz. This evaluation
compares the extracted F0 values from the original sound files to the ones
generated with each model. With the resulting differences, the root mean square
error is calculated to be able to assign each model a single score value. When
comparing specific extracted values of sound files, it is usually needed to use
dynamic time warping (DTW) to match the corresponding values to each other. In
our case this was not needed, as we already aligned each file using DTW before.
The reference value when comparing the original sound files with themselves, is
0.0 as there is no difference between them and therefore no error.

\subsubsection*{F0 RMSE results}
\begin{figure}[hbtp]
    \includegraphics[width=\textwidth]{evaluation/graphs/F0RMSE.png}
    \caption{Fundamental frequency root mean square error}
    \label{fig:f0rmse_results}
\end{figure}

@@

\subsubsection*{Speech-to-Noise ratio (SNR)}
The Speech-to-Noise ratio (SNR) compares the ratio of speech in a sound file, to
the amount of background noise. The formula used in this evaluation is \\
\[
    SNR = 10*log_{10} (\frac{RMSE(signal)}{RMSE(noise)})
\]
as formulated in \cite{ji2020comprehensivesurveydeepmusic}. The SNR is equal to 10 times the 10th log of the RMSE of
the original file (signal) divided by the RMSE of the generated file (noise). It
is usually measured in decibels (dB). The reference value for a perfect ratio is
0.0 as shown by comparing the original sound files to themselves.

\subsubsection*{SNR results}
\begin{figure}[hbtp]
    \includegraphics[width=\textwidth]{evaluation/graphs/SNR.png}
    \caption{Speech-to-noise ratio}
    \label{fig:snr}
\end{figure}

@@

%==============================================
%============= Mixing and Mastering ============
%==============================================
\section*{Mixing and Mastering}

%==============================================
%================ Conclusion ===================
%==============================================
\section*{Conclusion}

>>>>

\subsubsection{Manual Segmentation}

To include more data and improve model performance, we additionally included two live albums in our dataset. As many segments contained screaming from the audience, we went through them and cut out unwanted parts manually with Praat, a tool for speech analysis and phonetic research.

@@

%==============================================
%================ Evaluation ===================
%==============================================
\section{Evaluation}

\subsection{DiffSinger}
The base model we used for our training and synthesizing is DiffSinger. It is an
acoustic model, meaning it can map linguistik and symbolic input (like text or
notes) into acoustic features, used to generate actual audio. Acoustic features
include the most common feature mel-spectograms, but can also include linear
spectograms, F0 and pitch contour, and energy. It is also a variance model,
which is needed when trying to synthesize actual singing. A variance model
models the acoustic variations, for example pitch, energy and duration of sound.
The variance model predicts, based on the training data, how the voice features
should vary over time, based on the input. To avoid long computation time and
large resource needs, DiffSinger uses a shallow diffusion model. Traditional
diffusion models generate data, by starting with pure, random noise, and step by
step denoising it. This inference process is slow and takes many steps for just
a single generated sample. The shallow diffusion model used by DiffSinger is a
simpler and faster version of a full diffusion model. It uses fewer steps, but
often starts with a better starting point (for example a prediction from another
model). DiffSinger uses a non-diffusion model to predict a rough mel-spectogram
for the synthesized data, and refines it using the shallow diffusion model. By
using this technique, a lot of unnecessary steps, resources and computation time
are saved. Not using another model to make a first prediction would cause the
generated data to be a lot worse, since less steps are used and therefore less
noise is removed.

\subsection{Choosing a model}

@@

\subsection{Used files}
The following 14 segments were used in the evaluation:
\begin{itemize}
    \item Segment 22 from album 1, song 4
    \item Segment 3 from album 1, song 5
    \item Segment 1 from album 1, song 8
    \item Segment 22 from album 1, song 8
    \item Segment 5 from album 2, song 4
    \item Segment 7 from album 2, song 6
    \item Segment 17 from album 2, song 6
    \item Segment 1 from album 2, song 9
    \item Segment 7 from album 2, song 9
    \item Segment 3 from album 3, song 5
    \item Segment 13 from album 3, song 5
    \item Segment 1 from album 3, song 6
    \item Segment 10 from album 3. song 6
    \item Segment 8 from album 5, song 3
\end{itemize}

\subsection{Criteria}

@@

\subsubsection{Perceptual Evaluation of Speed Quality (PESQ)}
While the evaluation using SingMOS is considered a subjective evaluation, PESQ
is an objective Mean Opinion Score evaluation. The result of PESQ is usually a
score of the perceived speech quality on a scale of 1.0 to 4.5 (with narrowband,
4.64 with wideband), with a value of <2.0 representing a poor perceived speech
quality, which may be hard to understand. A value of about 3.0 is considered a
fair quality with some degradation, but generally understandable, and a value of
4.0 or more is considered excellent quality, with (almost) no degradation.
Although PESQ itself aligns both input files to account for timing mismatches,
it should be irrelevant in our case, as both input files are supposed to have
the same text, and everything was already aligned previously. The perceptual
part in PESQ refers to the way the sound files are analyzed. Instead of treating
every frequency and loudness the same, PESQ mimics the human ear and how an ear
is more sensitive to certain frequencies. The reference value for identical
files (comparing the original sound files with themselves), is approximately 4.64, as
expected.

\subsubsection{PESQ results}
\begin{figure}[hbtp]
    \includegraphics[width=\textwidth]{evaluation/graphs/PESQ.png}
    \caption{Perceptual Evaluation of Speech Quality results per model}
    \label{fig:pesq_results}
\end{figure}

@@

\subsubsection{F0 Root mean square error (F0 RMSE)}
The F0 value of speech, often also referred to as pitch or fundamental
frequency, is measured in Hertz, and describes the rate of vibration of the
vocal folds. The range of F0 is usually between 50 Hz to 450 Hz. This evaluation
compares the extracted F0 values from the original sound files to the ones
generated with each model. With the resulting differences, the root mean square
error is calculated to be able to assign each model a single score value. When
comparing specific extracted values of sound files, it is usually needed to use
dynamic time warping (DTW) to match the corresponding values to each other. In
our case this was not needed, as we already aligned each file using DTW before.
The reference value when comparing the original sound files with themselves, is
0.0 as there is no difference between them and therefore no error.

\subsubsection{F0 RMSE results}
\begin{figure}[hbtp]
    \includegraphics[width=\textwidth]{evaluation/graphs/F0RMSE.png}
    \caption{Fundamental frequency root mean square error}
    \label{fig:f0rmse_results}
\end{figure}

@@

\subsubsection{Speech-to-Noise ratio (SNR)}
The Speech-to-Noise ratio (SNR) compares the ratio of speech in a sound file, to
the amount of background noise. The formula used in this evaluation is \\
\[
    SNR = 10*log_{10} (\frac{RMSE(signal)}{RMSE(noise)})
\]
as formulated in \cite{ji2020comprehensivesurveydeepmusic}. The SNR is equal to 10 times the 10th log of the RMSE of
the original file (signal) divided by the RMSE of the generated file (noise). It
is usually measured in decibels (dB). The reference value for a perfect ratio is
0.0 as shown by comparing the original sound files to themselves.

\subsubsection{SNR results}
\begin{figure}[hbtp]
    \includegraphics[width=\textwidth]{evaluation/graphs/SNR.png}
    \caption{Speech-to-noise ratio}
    \label{fig:snr}
\end{figure}

@@

%==============================================
%============= Mixing and Mastering ============
%==============================================
\section{Mixing and Mastering}

%==============================================
%================ Conclusion ===================
%==============================================
\section{Conclusion}
